Speed and strength of an epidemic intervention

### 2020-06-27 doc/speedstrength.tex
merge with Daniel significance
good nght
move out significance

%% \usepackage{amsmath}
\usepackage{natbib}
\usepackage{hyperref}
\bibliographystyle{chicago}
\date{\today}

@@

\newcommand{\comment}{}
\renewcommand{\comment}[3]{\textcolor{#1}{\textbf{[#2: }\textit{#3}\textbf{]}}}
\renewcommand{\comment}[3]{}

@@

\section*{Significance statement}

The exponential growth rate $r$ (speed) and the reproductive number (strength) of an epidemic $\RR$ represent the speed and strength of an epidemic.
Even though both quantities have equally valid threshold values ($r=0$ and $\RR=1$) that determine whether a disease can spread in a population, disease modelers often measure the effectiveness of intervention by its ability to reduce $\RR$ below 1.
We generalize the classic, strength-based paradigm by defining the speed and strength of an intervention, which must be greater than their corresponding values of an epidemic to prevent its spread.
Both speed- and strength-based perspective can yield important, but different, biological insights into understanding the disease spread.

@@

\jd{For next version, consider making \figref{condom} a four-panel figure like \figref{test}.}

@@

\jd{Let's look at some GIs: high, medium and low \pEarly $\times$ intrinsic, backward}

>>>>

%% \usepackage{amsmath}
\usepackage{natbib}
\usepackage{hyperref}
\bibliographystyle{plain}
\date{\today}

@@

\newcommand{\comment}{RENEW}
\renewcommand{\comment}[3]{\textcolor{#1}{\textbf{[#2: }\textit{#3}\textbf{]}}}
\renewcommand{\comment}[3]{}

@@

@@

%% \jd{For next version, consider making \figref{condom} a four-panel figure like \figref{test}.}

@@

%% \jd{Let's look at some GIs: high, medium and low \pEarly $\times$ intrinsic, backward}
